Untitled

### 2023-08-11 draft_v0.Rmd
Explore top 3. From Windows.

>>>>

```{r}
# department, branch, section, code_group not helpful
dta_um %>% 
  group_by(code, cause_code) %>% 
  count() %>% 
  print(n = Inf)

# filter out cause codes "Not Defined" etc, but keep NA

dta_um <- dta_um %>% 
  filter(!cause_code %in% c("No Cause Found",
                           "None/Private") &
           !is.na(official_suburb))

dta_um %>% 
  group_by(official_suburb) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  print(n = 20)

# top 3 by month

plotdta <- dta_um %>% 
  group_by(year_creation, month_creation, official_suburb) %>% 
  count() %>% 
  arrange(year_creation, month_creation, desc(n)) %>% 
  print(n = 20) %>% 
  ungroup()

plotdta <- map(unique(plotdta$month_creation),
           ~plotdta %>% 
  filter(month_creation == .x) %>% 
  arrange(desc(n)) %>% 
  slice(1:10)) %>% 
    bind_rows()

dta_um %>% 
  group_by(official_suburb) %>% 
  count(name = "total_overall") %>% 
  inner_join(plotdta) %>% 
  ggplot(aes(n, official_suburb, fill = total_overall))+
  geom_col()+
  facet_wrap(~month_creation)

# START HERE
